\documentclass[a4paper,10pt]{article}  
\usepackage[a4paper,margin=0.5in]{geometry}  
\usepackage{enumitem}  
\usepackage{titlesec}  
\usepackage{hyperref}  
\usepackage{parskip}  

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]  
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}  

\hypersetup{  
    colorlinks=true,  
    linkcolor=black,  
    urlcolor=blue,  
}  

\begin{document}  

\begin{center}  
    \textbf{\huge Roshan Laharwani Sagar} \\  
    \texttt{roshanleharwani@gmail.com} | +91 74706 29602 \\  
    \href{https://linkedin.com/in/roshan-laharwani}{linkedin.com/in/roshan-laharwani} | \href{https://github.com/roshanleharwani}{github.com/roshanleharwani}  
\end{center}  

\section*{Technical Skills}  
\textbf{Languages:} Python, Java, JavaScript, TypeScript, HTML, CSS \\  
\textbf{Frameworks \& Libraries:} Flask, Express.js, Next.js, React.js, Flutter, Tailwind CSS \\  
\textbf{Databases:} MongoDB, MySQL, PostgreSQL \\  
\textbf{Tools \& Technologies:} Git, Docker, AWS, GCP  

\section*{Projects}  
\textbf{Packaged Food Product Report Generator with Barcode} \\  
\textit{GitHub: \href{https://github.com/ProjectClean}{github.com/ProjectClean}} \\  
- Developed a prototype integrating a barcode scanner, LCD, and ESP32 Wi-Fi module. \\  
- Created a Node.js server using Express.js to fetch ingredient details via the Open Food Facts API. \\  
- Employed LLaMA 3.1 70B (Groq API) for product data analysis and utilized EJS templating for report generation.  

\textbf{Team Recruitment Platform (CoLab)} \\  
\textit{GitHub: \href{https://github.com/CoLab}{github.com/CoLab}} \\  
- Designed a platform enabling students to post projects, specify required skills, and form teams. \\  
- Implemented request/acceptance workflows, user ratings, and leaderboards, enhancing collaboration efficiency by 30\%.  

\textbf{Stock and Market Sentiment Platform} \\  
- Achieved 90\% sentiment accuracy by aggregating and analyzing 250+ daily news articles over a 30-day window using FinBERT (Hugging Face). \\  
- Integrated FBProphet for stock forecasting, reducing error by 15\%, and developed a Market Mood Index for Sensex/Nifty50. \\  
- Managed over 100 requests per minute using Express.js for API and Flask for statistical analysis with a latency of 3 seconds.  

\section*{Experience}  
\textbf{Technical Team Lead, CodeCrux – VIT-AP} \hfill 2025 -- Present \\  
- Leading technical initiatives and mentoring team members to deliver web and AI-driven projects. \\  
- Overseeing project execution and ensuring alignment with the club’s innovation goals.  

\section*{Achievements}  
- Secured 2nd Place at GFG Hacktoberfest 2024. \\  
- Selected as a Top 5 Finalist at Google Dev Sprint 2025.  

\section*{Education}  
\textbf{VIT-AP University} \\  
B.Tech in Computer Science, Amaravati, A.P. \hfill 2023 -- 2027 \\  
CGPA: 8.94 / 10  

\textbf{Vatsalya Sr. Sec. School} \\  
Higher Secondary Education, Sagar, M.P. (CBSE) \hfill 2007 -- 2023 \\  
XII Percentage: 85.5\%  

\section*{Leadership \& Responsibilities}  
\textbf{Team Member, CSI Chapter (Team V-CODE) – VIT-AP} \hfill Jan 2023 -- Dec 2024 \\  
- Conducted the 100 Days of Java program, successfully training over 150 students in core Java.  

\end{document}